TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-22 paper/paper.tex
Added some more clarification referring to the BBR paper

This report includes a performance and behaviour analysis of different TCP congestion control algorithms in a (simulated) multitenant datacenter network. Based on the results, we will recommend datacenters on measures to take to keep providing a reliable environment for customers when multiple congestion control algorithms are active in the network, for example using Quality of Service or discouraging certain congestion control algorithms. The main research question is: {\it How can a datacenter provide a reliable and performing environment for customers when multiple TCP congestion control algorithms are used in the
network?}

@@

BBR is the best-performing algorithm in our set, because it barely responds to
packet loss. As mentioned in the results, we see no hard evidence that this
causes other algorithms to reduce their speed further, but there are slight
indications. For example in the test of DCTCP versus BBR, DCTCP reaches around
0.2 to 0.6 megabytes per second. In the test of DCTCP versus BIC, this is 0.3
to 0.7 megabytes per second. The difference is large nor statistically
significant, but it warrants looking into. On the scale of 0.7 megabytes per
second, a tenth of a megabyte does make a difference.

>>>>

This report includes a performance and behaviour analysis of different TCP congestion control algorithms in a (simulated) multitenant datacenter network. Mario Hock et al. describe in a paper that BBR shows unfair behaviour compared to the CUBIC congestion control algorithm \cite{bbr-congestion-comparison}. Therefore the fairness between TCP congestion control algorithms will also be included in the analysis. Based on the results, we will recommend datacenters on measures to take to keep providing a reliable environment for customers when multiple congestion control algorithms are active in the network, for example using Quality of Service or discouraging certain congestion control algorithms. The main research question is: {\it How can a datacenter provide a reliable and performing environment for customers when multiple TCP congestion control algorithms are used in the
network?}

@@

BBR is the best-performing algorithm in our set, because it barely responds to
packet loss. However, we were unable to reproduce the results written in the paper by Mario Hock et al \cite{bbr-congestion-comparison}. We used multiple values to simulate packet loss as well as delay, which simulate having small buffers. BBR is a TCP congestion control protocol that reacts to the minimum RTT in combination with the Bottleneck Bandwidth. We have tested multiple delay values that appear in the real world. The delay values are directly related to the minimum RTT possible on the link. As mentioned in the results, we see no hard evidence that this
causes other algorithms to reduce their speed further, but there are slight
indications. For example in the test of DCTCP versus BBR, DCTCP reaches around
0.2 to 0.6 megabytes per second. In the test of DCTCP versus BIC, this is 0.3
to 0.7 megabytes per second. The difference is large nor statistically
significant, but it warrants looking into. On the scale of 0.7 megabytes per
second, a tenth of a megabyte does make a difference.
